Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning

### 2016-08-10 Docs/IJES/journal.tex
[A-22] In page 9 (right column), "It [is] worth mentioning".
mark implemented comments using the blue color

Optimization is the act of obtaining the best result ({\it i.e.}, the optimal solution) under given circumstances as defined in~\cite{Rao2009}. There is no single method available for efficiently solving all optimization problems, according to~\cite{Rao2009}. The most well-known technique is linear programming, which is an method applicable for the solution of problems in which the objective function and the constraints appear as linear functions of the decision variables. A particular case of linear programming is ILP, in which the variables can assume just integer values. Eq.~\eqref{linear-programming-problem} shows a typical linear programming problem, where $A$ and $b$ are vectors from the objective function, while $Aeq$ and $beq$ are matrices that describe the linear equality constraints

@@

\begin{itemize}
\item{\textbf{maximize(T)}
this function instructs the solver that a given variable $T$ should be maximized, which includes real, integer, or bit-vector variables.}
\item{\textbf{minimize(T)}
this function instructs the solver that a given variable $T$ should be minimized, the accepted types are the same as maximize function.}
\item{\textbf{Assert-Soft F : weight n}
the function \textit{assert-soft} adds a restriction to $F$, which can also add a weight $n$; the default value is $1$.}
\end{itemize}

@@

A directed simple graph $ G = (V,E) $, called the task graph of the system, is given. Where the vertices $V = \{V_1,V_2,\dotso,V_n\}$ represent the nodes that are the components of the system that will be partitioned. The edges $E$ represent communication between components. Additionally, each node  $V_i$ has a cost $h(V_i)$ (or $h_i$) of hardware if implemented in hardware and a cost $s(V_i)$ (or $ s_i $) of software if implemented in software. Finally, $c(V_i,V_j)$ represents the communication cost between $V_i$ and $V_j$ if they are implemented in different contexts (hardware or software).

@@

\vspace{2 mm}
In particular, different optimization (and decision) problems can be defined for partitioning HW-SW, as described by~\cite{Arato2003}. In this paper, however, the focus is on systems with hard real-time constraints: $ S_0 $ is given (initial cost of software), {\it i.e.}, the goal is to find a $P$ HW-SW partitioning so that $ S_p \leq S_0 $ and $ H_p $ is minimal, which is thus related. Consequently, the constraints can be reformulated based on Equations~\eqref{linear-programming-problem} and~\eqref{software-communication-costs} as

@@

\vspace{2 mm}
\noindent where $s$ and $c$ are the vectors representing the cost functions, $E$ is the transposed incidence matrix of $G$ (indicating which edges cross the boundary between the contexts of hardware and software), and $x$ represents the decision variable (a binary vector indicating the partition: $1$ if the node is realized in hardware and $0$ if the node is realized in software). Concerning the complexity of this problem, \cite{Arato2003} demonstrate that it is NP-Hard, as defined in~\cite{Cormem}.

@@

The ESBMC algorithm starts with the declarations of hardware, software, and communication costs. $S_0$ must also be defined, as the transposed incidence matrix (used in Eq.~\eqref{hw-sw-partitioning}) and the identity matrix (necessary to work with the matrices), as typically done in MATLAB. Here, matrices $A$ and $b$ are generated. At that point, the ESBMC algorithm starts to differ from the ILP and GA presented in~\cite{Trindade2015}.

@@

\vspace{2 mm}
It is possible to instruct ESBMC with which type of values the variables must be tested. Therefore, there is a declaration to populate all decision variables $x$ with non-deterministic Boolean values. \textcolor{blue}{As a result, the Boolean value that is assigned to each decision variable $x_i$ is actually selected by the SMT Solver, during its solving phase, which checks once all possible combinations to yield a feasible solution, {\it e.g.}, by handling the terms in the given background theory using a decision procedure~\cite{DeMoura2008,Brummayer2009}. If this is achieved, the ASSUME directive ensures the compliance of the constraint $A.x \leq b$}.

@@

In the ESBMC algorithm, there is no need for adding slack variables in Eq.~\eqref{hw-sw-partitioning}, which reduces the number of variables to be solved if compared to ILP and GA.

@@

Finally, there are approaches that mixes heuristics with exact solution tools. The idea is to use a heuristic to speed up some phase of an exact solution tool. It is worth mentioning that the final solution is not necessarily an optimal global solution. Only the SMT-based verification is guaranteed to find the exact solution, but hybrid algorithms are faster when complexity rises.

>>>>

Optimization is the act of obtaining the best result ({\it i.e.}, the optimal solution) under given circumstances as defined in~\cite{Rao2009}. There is no single method available for efficiently solving all optimization problems, according to~\cite{Rao2009}. The most well-known technique is linear programming, which is an method applicable for the solution of problems in which the objective function and the constraints appear as linear functions of the decision variables. A particular case of linear programming is ILP, in which the variables can assume just integer values. \textcolor{blue}{Eq.~\eqref{linear-programming-problem} shows a typical linear programming problem, where $A$ and $b$ are vectors from the objective function, while $Aeq$ and $beq$ are matrices that describe the linear equality constraints}

@@

\begin{itemize}
\item{\textbf{maximize(T)}
\textcolor{blue}{this function instructs the solver that a given variable $T$ should be maximized, which includes real, integer, or bit-vector variables.}}
\item{\textbf{minimize(T)}
\textcolor{blue}{this function instructs the solver that a given variable $T$ should be minimized, the accepted types are the same as maximize function.}}
\item{\textbf{Assert-Soft F : weight n}
the function \textit{assert-soft} adds a restriction to $F$, which can also add a weight $n$; the default value is $1$.}
\end{itemize}

@@

\textcolor{blue}{A directed simple graph $ G = (V,E) $, called the task graph of the system, is given. Where the vertices $V = \{V_1,V_2,\dotso,V_n\}$ represent the nodes that are the components of the system that will be partitioned. The edges $E$ represent communication between components. Additionally, each node  $V_i$ has a cost $h(V_i)$ (or $h_i$) of hardware if implemented in hardware and a cost $s(V_i)$ (or $ s_i $) of software if implemented in software. Finally, $c(V_i,V_j)$ represents the communication cost between $V_i$ and $V_j$ if they are implemented in different contexts (hardware or software).}

@@

\vspace{2 mm}
\textcolor{blue}{In particular, different optimization (and decision) problems can be defined for partitioning HW-SW, as described by~\cite{Arato2003}. In this paper, however, the focus is on systems with hard real-time constraints: $ S_0 $ is given (initial cost of software), {\it i.e.}, the goal is to find a $P$ HW-SW partitioning so that $ S_p \leq S_0 $ and $ H_p $ is minimal, which is thus related. Consequently, the constraints can be reformulated based on Equations~\eqref{linear-programming-problem} and~\eqref{software-communication-costs} as}

@@

\vspace{2 mm}
\noindent \textcolor{blue}{ where $s$ and $c$ are the vectors representing the cost functions, $E$ is the transposed incidence matrix of $G$ (indicating which edges cross the boundary between the contexts of hardware and software), and $x$ represents the decision variable (a binary vector indicating the partition: $1$ if the node is realized in hardware and $0$ if the node is realized in software)}. Concerning the complexity of this problem, \cite{Arato2003} demonstrate that it is NP-Hard, as defined in~\cite{Cormem}.

@@

\textcolor{blue}{The ESBMC algorithm starts with the declarations of hardware, software, and communication costs. $S_0$ must also be defined, as the transposed incidence matrix (used in Eq.~\eqref{hw-sw-partitioning}) and the identity matrix (necessary to work with the matrices), as typically done in MATLAB.} Here, matrices $A$ and $b$ are generated. At that point, the ESBMC algorithm starts to differ from the ILP and GA presented in~\cite{Trindade2015}.

@@

\vspace{2 mm}
\textcolor{blue}{It is possible to instruct ESBMC with which type of values the variables must be tested. Therefore, there is a declaration to populate all decision variables $x$ with non-deterministic Boolean values. As a result, the Boolean value that is assigned to each decision variable $x_i$ is actually selected by the SMT Solver, during its solving phase, which checks once all possible combinations to yield a feasible solution, {\it e.g.}, by handling the terms in the given background theory using a decision procedure~\cite{DeMoura2008,Brummayer2009}. If this is achieved, the ASSUME directive ensures the compliance of the constraint $A.x \leq b$}.

@@

\textcolor{blue}{In the ESBMC algorithm, there is no need for adding slack variables in Eq.~\eqref{hw-sw-partitioning}, which reduces the number of variables to be solved if compared to ILP and GA.}

@@

Finally, there are approaches that mixes heuristics with exact solution tools. The idea is to use a heuristic to speed up some phase of an exact solution tool. \textcolor{blue}{It is worth mentioning} that the final solution is not necessarily an optimal global solution. Only the SMT-based verification is guaranteed to find the exact solution, but hybrid algorithms are faster when complexity rises.
